\cvsection{Experience}

\vspace{0.5cm}

\begin{cventries}
  \cventry
    {Central Kitchen of mermoz High School}
    {Internship Bioengineering 3\textsuperscript{rd} Year Nutrition}
    {Montpellier, France}
    {Apr. - Jul. 2016}
    {
      \begin{cvitems}
        \item {Studied and balanced the meals of the sports students.}
        \item {Designed and organized thematic workshops with sports students.}
        \item {Identified and analyzed new catering markets for the renewal of the kitchen’s products.}
        \item {Implemented the devised diet plans in accordance to the nutrition standards of healthcare.}
      \end{cvitems}
    }
    {José Clément - \href{mailto:jose.clement@ac-montpellier.fr}{jose.clement@ac-montpellier.fr}}
  \cventry
    {University Institute of Technology of Montpellier}
    {Project ``Paniers Végétalité''}
    {Montpellier, France}
    {Oct. 2015 - Apr. 2016}
    {
      \begin{cvitems}
        \item {Goal: Set up a distribution of baskets of fruits and vegetables, at an affordable price for the students, on the campus of Montpellier.}
        \item {Researched for similar projects already set up in other cities.}
        \item {Analyzed and negotiated the proposed offers after contacting agencies and producers which could support our project.}
        \item {
            Promoted the project on social networks, created a website (
            \href
                {http://blablaplat.jimdo.com/panier-végétalité-fruits-légumes/}
                {http://blablaplat.jimdo.com/panier-végétalité-fruits-légumes/}
            ).
        }
        \item {Dealt with the orders and organized the deliveries.}
        \item {Established a partnership with a local producer of fruits and vegetables (
            \href
                {http://croquez-du-frais.fr/}
                {http://croquez-du-frais.fr/}
            ).
        }
        \item {Success of this project: weekly deliveries of well-diversified baskets of fruits and vegetables to the students at the affordable price of 5 euros (less than \$6).}
      \end{cvitems}
    }
    {Virginie Masdoua - \href{mailto:virginie.masdoua@wanadoo.fr}{virginie.masdoua@wanadoo.fr}}
  \cventry
    {Pediatric Service - Children's Hospital of Nancy}
    {2\textsuperscript{nd} Trainee Dietitian-Nutritionist}
    {Nancy, France}
    {Jun. - Jul. 2015}
    {
      \begin{cvitems}
        \item {Designed personalized programs for nutrition of children suffering from pathologies.}
        \item {Calculated the patients' needs for the implementation of their ketogenic diets.}
        \item {Explained the ketogenic diet to the patients through therapeutic education.}
        \item {Ordered meals for immunosuppressed patients.}
        \item {Attented meetings on metabolic diseases.}
      \end{cvitems}
    }
    {Elisabeth Favre - \href{mailto:e.favre@chu-nancy.fr}{e.favre@chu-nancy.fr}}
  \cventry
    {Care Center of Consequences and Rehabilitation}
    {1\textsuperscript{st} Trainee Dietitian-Nutritionist}
    {Trois-Épis, France}
    {Apr. - Jun. 2015}
    {
      \begin{cvitems}
        \item {Charged with care of patients with various needs (digestive surgery, geriatrics, eating disorders, etc.).}
        \item {Performed nutritional balance assessment and developed care plans for patients affected by obesity.}
        \item {Helped to run nutritional educational workshops intended for the patients.}
      \end{cvitems}
    }
    {Catherine Scandella - \href{mailto:cscandella@mgen.fr}{cscandella@mgen.fr}}
  \cventry
    {Nursing home}
    {Trainee Dietitian in Institutional Catering}
    {Longwy, France}
    {Oct. 2014}
    {
      \begin{cvitems}
        \item {Learned the functioning of a kitchen in institutional catering.}
        \item {Participated in the various stages of production of dishes.}
        \item {Analyzed the hygiene and food safety.}
      \end{cvitems}
    }
    {}
\end{cventries}

\clearpage